Democracy, Public Support, and Measurement Uncertainty

### 2021-07-07 paper/dcpo_demsupport.Rmd
update moc estimates @sammo3182

@@

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Liberal Democracy (Vdem)") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
    scale_color_gb(palette = "digitMixed") +
    facet_wrap(~ type)

@@

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Public Support for Democracy") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
    scale_color_gb(palette = "digitMixed") +
    facet_wrap( ~ type)

@@

# Replication with Alternative Methods Accounting for Uncertainty
```{r MocclaassenUncertaintyAJPS}
load(here("data","cls_ajps.rda"))

df_cls <- purrr::map(1:900, function(anEntry) {
  cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

ls_iv <- c("plm::lag(SupDem_trim, 1)",                         
           "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1) ") ##all use trim
ls_method <- c("plm", "pgmm")
ls_eq <- glue("Libdem_VD ~ plm::lag(Libdem_VD, 1:2) + {ls_iv} + 
              plm::lag(lnGDP_imp, 1) + plm::lag(GDP_imp_grth, 1) + 
              plm::lag(Libdem_regUN, 1) + plm::lag(Pr_Muslim, 1) + plm::lag(Res_cp_WDI_di, 1)")

ls_mod <- c(
  glue("plm({ls_eq}, model = 'pooling', data = aData)"),
  glue(
    "pgmm({ls_eq} | plm::lag(Libdem_VD, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
  )
)

result_clsUncertain  <- map(ls_mod[1:2], function(aMod){
  result <- methodComposition1(df_cls,aMod)
})

names(result_clsUncertain) <- c("pooled", "pooled-regime")

result_clsUncertain_gmm  <- map(ls_mod[3:4], function(aMod){
  result <- methodComposition2(df_cls,aMod)
})
names(result_clsUncertain_gmm) <- c("gmm", "gmm-regime")

result_clsUncertain_whole <- append(result_clsUncertain, result_clsUncertain_gmm)

saveRDS(result_clsUncertain_whole, file =here("output","clsAJPS_uncertainty.RDS"))

@@

```{r MocdcpoUncertaintyAJPS}
load(here("data","dcpo_ajps.rda"))

df_dcpo <- purrr::map(1:900, function(anEntry) {
  dcpo_ajps[[anEntry]] %>%     #original data has include theta_dem_trim
    plm::pdata.frame(index = c("country", "year"))
})

ls_iv <- c("plm::lag(theta_trim, 1)", 
           "plm::lag(theta_dem_trim, 1) + plm::lag(theta_aut_trim, 1)") #use trimed data
ls_method <- c("plm", "pgmm")
ls_eq <- glue("Vdem_libdem ~ plm::lag(Vdem_libdem, 1:2) + {ls_iv} + plm::lag(lg_imp_mdpgdp, 1) + plm::lag(mdprgdp_grwth, 1) + plm::lag(Region_libdem, 1) + plm::lag(muslism_prop_2010, 1) + plm::lag(dependence_pc_di, 1)") 
ls_mod <- c(
  glue("plm({ls_eq}, model = 'pooling', data = aData)"),
  glue(
    "pgmm({ls_eq} | plm::lag(Vdem_libdem, 3:5), data = aData, effect='individual', model='onestep', transformation='ld', indexes=c('country', 'year'))"
  )
)

result_dcpoUncertain  <- map(ls_mod[1:2], function(aMod){
  result <- methodComposition1(df_dcpo,aMod)
})

names(result_dcpoUncertain) <- c("pooled", "pooled-regime")

result_dcpoUncertain_gmm  <- map(ls_mod[3:4], function(aMod){
  result <- methodComposition2(df_dcpo,aMod)
})

names(result_dcpoUncertain_gmm) <- c("gmm", "gmm-regime")

result_dcpoUncertain_whole <- append(result_dcpoUncertain, result_dcpoUncertain_gmm)

saveRDS(result_dcpoUncertain_whole, file =here("output","dcpoAJPS_uncertainty.RDS"))

@@

```{r visualizedMocUncertainAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}

result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsUncertain_whole <- readRDS(here("output", "clsAJPS_uncertainty.RDS"))
result_dcpoUncertain_whole <- readRDS(here("output", "dcpoAJPS_uncertainty.RDS"))

result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Claassen 2020a"),
  mutate(MOCsumm(result_clsUncertain_whole[["pooled"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm(result_dcpoUncertain_whole[["pooled"]]), model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Claassen 2020a"),
  mutate(MOCsumm(result_clsUncertain_whole[["gmm"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm(result_dcpoUncertain_whole[["gmm"]]), model = "DCPO")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a", "Claassen w/uncertainty", "DCPO")))

@@

###########Regime
result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Claassen 2020a"),
  mutate(MOCsumm(result_clsUncertain_whole[["pooled-regime"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm(result_dcpoUncertain_whole[["pooled-regime"]]), model = "DCPO")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Claassen 2020a"),
  mutate(MOCsumm(result_clsUncertain_whole[["gmm-regime"]]), model = "Claassen w/uncertainty"),
    mutate(MOCsumm(result_dcpoUncertain_whole[["gmm-regime"]]), model = "DCPO")
)%>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Claassen 2020a","Claassen w/uncertainty", "DCPO")))
terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))
plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())
legend <- get_legend(plot_AJPS2)
plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)

@@

```{r claassenMocUncertaintyAPSR}
load(here("data", "pure_cls_apsr.rda")) #use pure_cls_apsr instead of cls_apsr
load(here("data", "exp_cls_apsr.rda")) #use exp_cls_apsr instead of cls_apsr

df_clsAPSR <- purrr::map(1:900, function(anEntry) {
  pure_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

df_our_clsAPSR <- purrr::map(1:900, function(anEntry) {
  exp_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

ls_eqECM <- glue("diff(SupDem_trim, lag = 1) ~ plm::lag(SupDem_trim, 1:2) + {ls_ivECM} + diff(lnGDP_imp, lag = 1) + plm::lag(lnGDP_imp, 1)") %>% 
  outer(ls_ctrlECM, paste0) %>% 
  as.vector() ##Change theta to SupDem_trim

ls_ivFD <- c("Libdem_z",
             "Polyarchy_z + Liberal_z")
ls_ctrlFD <- c("", " + Corrup_TI_z")
ls_eqFD <- glue("SupDem_trim ~ {ls_ivFD} + lnGDP_imp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()
ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
)

result_clsUncertain  <- map(ls_mod, function(aMod){
  result <- methodComposition3(df_clsAPSR,aMod)
})  #claassen's data

result_our_clsUncertain  <- map(ls_mod, function(aMod){
  result <- methodComposition3(df_our_clsAPSR,aMod)
})   ##our expanded data

names(result_clsUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

names(result_our_clsUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_clsUncertain, file = here::here("ouput","clsAPSR_uncertainty.RDS"))

saveRDS(result_our_clsUncertain, file = here::here("ouput","our_clsAPSR_uncertainty.RDS"))

@@

```{r  dcpoMocUncertaintyAPSR}
load(here("data","dcpo_apsr.rda"))
df_dcpoUncertainAPSR <- purrr::map(1:900, function(anEntry) {
  dcpo_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

ls_ivECM <- c("diff(Vdem_libdem_z, lag = 1) + plm::lag(Vdem_libdem_z, 1)", 
              "diff(Vdem_polyarchy_z, lag = 1) + plm::lag(Vdem_polyarchy_z, 1) + diff(Vdem_liberal_z, lag = 1) + plm::lag(Vdem_liberal_z, 1)")
ls_ctrlECM <- c("", " + diff(corruption_z, lag = 1) + plm::lag(corruption_z, 1)")
ls_eqECM <- glue("diff(theta_trim, lag = 1) ~ plm::lag(theta_trim, 1:2) + {ls_ivECM} + diff(lg_imp_mdpgdp, lag = 1) + plm::lag(lg_imp_mdpgdp, 1)") %>% 
  outer(ls_ctrlECM, paste0) %>% 
  as.vector()

ls_ivFD <- c("Vdem_libdem_z",
             "Vdem_polyarchy_z + Vdem_liberal_z")
ls_ctrlFD <- c("", " + corruption_z")
ls_eqFD <- glue("theta_trim ~ {ls_ivFD} + lg_imp_mdpgdp") %>% 
  outer(ls_ctrlFD, paste0) %>% 
  as.vector()

ls_mod <- c(
  glue("plm({ls_eqECM}, model = 'pooling', data = aData)"),
  glue("plm({ls_eqFD}, model = 'fd', index = 'country', data = aData)")
)

result_dcpoUncertain  <- map(ls_mod, function(aMod){
  result <- methodComposition3(df_dcpoUncertainAPSR,aMod)
})

names(result_dcpoUncertain) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(result_dcpoUncertain, file =here("output","dcpoAPSR_uncertainty.RDS"))

@@

```{r visualizedMocUncertainAPSR, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}

#result_clsUncertain <- readRDS(here("output","clsAPSR_uncertainty.RDS"))
result_clsUncertain <- readRDS(here("output","our_clsAPSR_uncertainty.RDS"))
result_dcpoUncertain <- readRDS(here("output","dcpoAPSR_uncertainty.RDS"))
result_clsAPSR <- readRDS(here("output","estimates_clsMeanAPSR.RDS"))

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Claassen 2020b"),
  mutate(MOCsumm2(result_clsUncertain[["pooled1"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm2(result_dcpoUncertain[["pooled1"]]), model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Claassen 2020b"),
  mutate(MOCsumm2(result_clsUncertain[["fd1"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm2(result_dcpoUncertain[["fd1"]]), model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020b","Claassen w/uncertainty", "DCPO"))
  )

@@

############################ Regime specified####
result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Claassen 2020b"),
  mutate(MOCsumm2(result_clsUncertain[["pooled-regime1"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm2(result_dcpoUncertain[["pooled-regime1"]]), model = "DCPO")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Claassen 2020b"),
  mutate(MOCsumm2(result_clsUncertain[["fd-regime1"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm2(result_dcpoUncertain[["fd-regime1"]]), model = "DCPO")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Claassen 2020b","Claassen w/uncertainty", "DCPO"))
  )
terms3 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Claassen 2020b"),
  mutate(MOCsumm2(result_clsUncertain[["pooled2"]]), model = "Claassen w/uncertainty"),
  mutate(MOCsumm2(result_dcpoUncertain[["pooled2"]]), model = "DCPO")
) %>% 
  mutate(type = "ECM")

>>>>

mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))

@@

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Liberal Democracy (Vdem)") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
    #scale_color_gb(palette = "digitMixed") +
    facet_wrap(~ type)

@@

dwplot(df_plot) +
    geom_vline(xintercept = 0,
               colour = "grey80",
               linetype = 2) +
    theme_minimal() +
    ggtitle("DV: Public Support for Democracy") +
    xlab("Coefficient Estimate") +
    theme(
        axis.title.y = element_blank(),
        legend.position = "bottom",
        legend.title = element_blank()
    ) +
    scale_y_discrete(labels = parse(text = rev(levels(df_plot$term)))) +
    # Using expressions of underscore and greek letters
   # scale_color_gb(palette = "digitMixed") +
    facet_wrap( ~ type)

@@

# Replication with Alternative Methods Accounting for Uncertainty
```{r moc_estimates}

result_clsAJPS <- readRDS(here("output", "estimates_clsMeanAJPS.RDS"))
result_clsAPSR <- readRDS(here("output", "estimates_clsMeanAPSR.RDS"))
mocresult_pureAJPS <- readRDS(here("output", "estimates_moc_pureAJPS.RDS"))
mocresult_expAJPS <- readRDS(here("output", "estimates_moc_expAJPS.RDS"))
mocresult_pureAPSR <- readRDS(here("output", "estimates_moc_pureAPSR.RDS"))
mocresult_expAPSR <- readRDS(here("output", "estimates_moc_expAPSR.RDS"))

@@

@@

```{r mocresult-pureAJPS}

df_pure_clsAjps <- purrr::map(1:900, function(anEntry) {
  pure_cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_pure_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
  result <- methodComposition1(df_pure_clsAjps,aMod)
})

names(result_pure_clsUncertain) <- c("pooled", "pooled-regime")

result_pure_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
  result <- methodComposition2(df_pure_clsAjps,aMod)
})
names(result_pure_clsUncertain_gmm) <- c("gmm", "gmm-regime")

mocresult_pureAJPS <- append(result_pure_clsUncertain, result_pure_clsUncertain_gmm)

saveRDS(mocresult_pureAJPS, file =here("output","estimates_moc_pureAJPS.RDS"))

```{r mocresult-expAJPS}

df_exp_clsAjps <- purrr::map(1:900, function(anEntry) {
  exp_cls_ajps[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
})

result_exp_clsUncertain  <- map(ls_mod_ajpsCLS[1:2], function(aMod){
  result <- methodComposition1(df_exp_clsAjps,aMod)
})

names(result_exp_clsUncertain) <- c("pooled", "pooled-regime")

result_exp_clsUncertain_gmm  <- map(ls_mod_ajpsCLS[3:4], function(aMod){
  result <- methodComposition2(df_exp_clsAjps,aMod)
})
names(result_exp_clsUncertain_gmm) <- c("gmm", "gmm-regime")

mocresult_expAJPS <- append(result_exp_clsUncertain, result_exp_clsUncertain_gmm)

saveRDS(mocresult_expAJPS, file =here("output","estimates_moc_expAJPS.RDS"))

```{r plot-mocAJPS, fig.cap= "The Effect of Public Support on Democracy ", eval = TRUE, fig.width=7, fig.height=10}

result_pooled <- bind_rows(
  mutate(result_clsAJPS[["pooled"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_pureAJPS[["pooled"]]), model = "Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

result_gmm <- bind_rows(
  mutate(result_clsAJPS[["gmm"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_pureAJPS[["gmm"]]), model = "Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["gmm"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "GMM")

result_pooledAJPS <- bind_rows(result_pooled, result_gmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original", "Uncertainty", "Uncertainty+Expanded Data")))

@@

###########Regime
result_regime <- bind_rows(
  mutate(result_clsAJPS[["pooled-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_pureAJPS[["pooled-regime"]]), model = "Uncertainty"),
  mutate(MOCsumm(mocresult_expAJPS[["pooled-regime"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "Pooled")

result_regimeGmm <- bind_rows(
  mutate(result_clsAJPS[["gmm-regime"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm(mocresult_pureAJPS[["gmm-regime"]]), model = "Uncertainty"),
 mutate(MOCsumm(mocresult_expAJPS[["gmm-regime"]]), model = "Uncertainty+Expanded Data")
)%>% 
  mutate(type = "GMM")

result_regimeAJPS <- bind_rows(result_regime, result_regimeGmm) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = rep(
      c("Democracy\n (t-1)",
        "Democracy\n (t-2)",
        "Support\n demo only\n (t-1)",
        "Support\n auto only\n (t-1)",
        "Log GDP\n per capita\n (t-1)",
        "GDP per\n capita growth\n (t-1)",
        "Regional\n democracy\n (t-1)",
        "Percent\n Muslim\n (t-1)",
        "Resource\n dependence\n (t-1)"),
      time = 6), 
    type = factor(type, levels = c("Pooled", "GMM")),
    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data")))
terms2 <- factor(rev(c("Democracy[t-1]",
                       "Democracy[t-2]",
                       "Support[t-1] (democracies~only)",
                       "Support[t-1] (autocracies~only)",
                       "Log~GDP~per~capita[t-1]",
                       "GDP~per~capita~growth[t-1]",
                       "Regional~democracy[t-1]",
                       "Percent~Muslim[t-1]",
                       "Resource~dependence[t-1]")), levels =
                   rev(c("Democracy[t-1]",
                         "Democracy[t-2]",
                         "Support[t-1] (democracies~only)",
                         "Support[t-1] (autocracies~only)",
                         "Log~GDP~per~capita[t-1]",
                         "GDP~per~capita~growth[t-1]",
                         "Regional~democracy[t-1]",
                         "Percent~Muslim[t-1]",
                         "Resource~dependence[t-1]")))
plot_AJPS2 <- dwplot(result_regimeAJPS, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms2))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  labs(
    title = "",
    subtitle = "Regime Specific"
  ) +
  facet_wrap(~type, scales = "free_x") +
  theme(legend.position = "bottom", 
        legend.title = element_blank())
legend <- get_legend(plot_AJPS2)
plot_AJPS2 <- plot_AJPS2 + theme(legend.position = "none")
grid.arrange(plot_AJPS1, plot_AJPS2, legend, ncol = 1)

@@

```{r mocresult-pureAPSR}

df_pure_clsAPSR <- purrr::map(1:900, function(anEntry) {
  pure_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

mocresult_pureAPSR  <- map(ls_mod_apsrCLS, function(aMod){
  result <- methodComposition3(df_pure_clsAPSR,aMod)
})

names(mocresult_pureAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(mocresult_pureAPSR, file = here::here("ouput","estimates_moc_pureAPSR.RDS"))

@@

```{r mocresult-expAPSR}

df_exp_clsAPSR <- purrr::map(1:900, function(anEntry) {
  exp_cls_apsr[[anEntry]] %>% 
    plm::pdata.frame(index = c("country", "year"))
}
)

mocresult_expAPSR <- map(ls_mod_apsrCLS, function(aMod){
  result <- methodComposition3(df_exp_clsAPSR,aMod)
})

names(mocresult_expAPSR) <- c("pooled1", "pooled-regime1", "pooled2", "pooled-regime2",
                                "fd1", "fd-regime1", "fd2", "fd-regime2")

saveRDS(mocresult_expAPSR, file = here::here("ouput","estimates_moc_expAPSR.RDS"))

@@

```{r plot-mocAJPS, fig.cap= "The Effect of Democracy on Public Support", eval = TRUE, fig.width=7, fig.height=10}

result_ecm1 <- bind_rows(
  mutate(result_clsAPSR[["pooled1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["pooled1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fd1 <- bind_rows(
  mutate(result_clsAPSR[["fd1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["fd1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_APSR1 <- bind_rows(result_ecm1, result_fd1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Liberal Democracy\n (Difference)",
        "Liberal Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Liberal Democracy\n (Difference)", 
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data"))
  )

@@

############################ Regime specified####

result_ecmReg1 <- bind_rows(
  mutate(result_clsAPSR[["pooled-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["pooled-regime1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled-regime1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fdReg1 <- bind_rows(
  mutate(result_clsAPSR[["fd-regime1"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["fd-regime1"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd-regime1"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")

result_RegAPSR1 <- bind_rows(result_ecmReg1, result_fdReg1) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = c(rep(
      c("Democratic Mood\n (t-1)",
        "Democratic Mood\n (t-2)",
        "Electoral Democracy\n (Difference)",
        "Electoral Democracy\n (t-1)",
        "Minoritarian Democracy\n (Difference)",
        "Minoritarian Democracy\n (t-1)",
        "Log GDP\n per capita\n (Difference)",
        "Log GDP\n (t-1)"),
      time = 3),
      rep(
        c("Electoral Democracy\n (Difference)", 
          "Minoritarian Democracy\n (Difference)",
          "Log GDP\n per capita\n (Difference)"), 
        time = 3
      )),
    type = factor(type,  levels = c("ECM", "First Difference")),
    model = factor(model, levels = c("Original","Uncertainty", "Uncertainty+Expanded Data"))
  )
terms3 <- factor(rev(c("Support[t-1]",
                       "Support[t-2]",
                       "Delta~Electoral~democracy",
                       "Electoral~democracy[t-1]",
                       "Delta~Minoritarian~democracy",
                       "Minoritarian~democracy[t-1]",
                       "Delta~Log~GDP~per~capita",
                       "Log~GDP[t-1]")),
                 levels = rev(c("Support[t-1]",
                                "Support[t-2]",
                                "Delta~Electoral~democracy",
                                "Electoral~democracy[t-1]",
                                "Delta~Minoritarian~democracy",
                                "Minoritarian~democracy[t-1]",
                                "Delta~Log~GDP~per~capita",
                                "Log~GDP[t-1]")))
plot_RegAPSR1 <- dwplot(result_RegAPSR1, dodge_size = 0.8, by_2sd = FALSE) +
  scale_y_discrete(labels = parse(text = levels(terms3))) +
  scale_color_grey(start = 0.4, end = 0.8, guide = guide_legend(reverse = TRUE)) +
  # scale_color_uiowa(name = "", palette = "digitMixed") +
  labs(
    title = "",
    subtitle = "Regime Specified"
  ) +
  facet_wrap(~type, scales = "free_x") + 
  theme(legend.position = "none")

@@

result_ecm2 <- bind_rows(
  mutate(result_clsAPSR[["pooled2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["pooled2"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["pooled2"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "ECM")

result_fd2 <- bind_rows(
  mutate(result_clsAPSR[["fd2"]][[1]][,1:3], model = "Original"),
  mutate(MOCsumm2(mocresult_pureAPSR[["fd2"]]), model = "Uncertainty"),
  mutate(MOCsumm2(mocresult_expAPSR[["fd2"]]), model = "Uncertainty+Expanded Data")
) %>% 
  mutate(type = "First Difference")
